Stateless Model Checking with Data-Race Preemption Points

### 2015-11-11 pldi-16/paper.tex
add structural text
somecleanup

\section{Conclusion}

@@

Our evaluation shows that \quicksand~achieves better bug-finding results than either single-pass data-race detection or single-state-space model checking (SSS-MC) alone.
We dramatically reduce false-positive data race reports,
%by verifying the absence of bugs in their associated state spaces
and find bugs caused by nondeterministic data-races in alternate thread interleavings missed entirely by single-pass analysis.
% TODO: Not true; Replace instead with a claim about partial verification.
Compared to SSS-MC, we find bugs faster in smaller subset state spaces,
%when the maximal state space is too large to explore
and find new bugs with data-race PPs that the maximal state space would not expose at all.

@@

% TODO: Make data set, at least, public.
TODO: Data set at least can be public.

@@

%Many thanks to David A. Eckhardt, Vaishaal Shankar, and Haryadi Gunawi for generously providing student implementations from CMU's, Berkeley's, and U. of Chicago's OS classes respectively.
Many thanks to Vaishaal Shankar, Haryadi Gunawi, and David A. Eckhardt for generously providing student implementations from Berkeley's, U. of Chicago's, and CMU's OS classes respectively.
Thanks to Wind River for the use of their simulator \simics.
Thanks to
% TODO: Post-double-blind-review
% Ji\v{r}\'{i} \v{S}im\v{s}a, John Wilkes, and
the anonymous PLDI reviewers for their helpful comments.
This work was supported in part by % TODO: funding sources
the U.S. Army Research Office under grant number W911NF0910273.

>>>>

\section{Conclusion}
\label{sec:conclusion}

@@

Our evaluation shows that \quicksand~achieves better bug-finding results than either single-pass data-race detection or single-state-space model checking (SSS-MC) alone.
%We dramatically reduce false-positive data race reports,
%%by verifying the absence of bugs in their associated state spaces
%and find bugs caused by nondeterministic data-races in alternate thread interleavings missed entirely by single-pass analysis.
% TODO: Not true; Replace instead with a claim about partial verification.
Compared to SSS-MC, we find bugs faster in smaller subset state spaces,
%when the maximal state space is too large to explore
and find new bugs with data-race PPs that the maximal state space would not expose at all.
Moreover, for tests where all state spaces with data-race PPs can be completed, we provide an equally strong verification as if every single instruction had been used as a PP.

@@

% TODO: Make data set, at least, public.

@@

Many thanks to Vaishaal Shankar, Haryadi Gunawi, and David A. Eckhardt for generously providing student implementations from Berkeley's, U. of Chicago's, and CMU's OS classes respectively.
Thanks to Wind River for the use of their simulator \simics.
Thanks to
% TODO: Post-double-blind-review
% Ji\v{r}\'{i} \v{S}im\v{s}a, John Wilkes, and
the anonymous PLDI reviewers for their helpful comments.
This work was supported in part by
the U.S. Army Research Office under grant number W911NF0910273.

### 2015-11-11 pldi-16/related.tex
some rephrasing and start to make a big table
add structural text
somecleanup

\section{Related Work}

@@

%Too many related projects to list have made contributions to the
Many advances have been made on the false-positive data race problem first introduced in \cite{eraser}.
\cite{hybriddatarace} and \cite{tsan} combine the lockset and happens-before analyses into a hybrid technique, which we employ.
% TODO: any more?
DroidRacer \cite{droidracer} and CAFA \cite{cafa} extend the analysis to event-driven Android applications, using domain-specific heuristics (orthogonal to our method) to reduce false positives. % cut for space?
% No, IDGAF about pure happens before.
%FastTrack \cite{fasttrack} optimizes the performance of pure happens-

@@

Portend \cite{portend} is the most closely related work we have found.
% FIXME: "limited"?
Based on single-pass data race reports, it explores a limited state space to classify candidates in a taxonomy of likely severity.
Compared to us, Portend additionally finds non-failing races which nevertheless cause
%suspiciously
different program output, while we depend on directly detecting failures.
It uses symbolic execution to test input nondeterminism as well as schedule nondeterminism,
while we explore the latter only.
However, Portend does not test alternate interleavings {\em in advance} of knowing data races,
which is necessary to expose some bugs (\sect{\ref{sec:eval-falseneg}}).
% XXX: Is this true??
It also assumes the POSIX synchronization API, so cannot verify arbitrary synchronization algorithms such as we do with \mxtest.
Future work could combine the two approaches, using MC to produce new data-race traces for Portend to classify, or using Portend's analysis to inform \quicksand's state space priorities.

@@

% TODO: talk about data race detectors???
% eg Scalable Race Detection for Android Applications -- uses domain specific heuristics to filter out false positives

>>>>

\section{Related Work}
\label{sec:related}

@@

%Too many related projects to list have made contributions to the
Many advances have been made on the false-positive data race problem since it was first introduced in \cite{eraser}.
\cite{hybriddatarace} and \cite{tsan} combine the lockset and happens-before analyses into a hybrid technique, which we employ.
% TODO: any more?
DroidRacer \cite{droidracer} and CAFA \cite{cafa} extend the analysis to event-driven Android applications, using domain-specific heuristics (orthogonal to our method) to reduce false positives. % cut for space?
% No, IDGAF about pure happens before.
%FastTrack \cite{fasttrack} optimizes the performance of pure happens-

@@

Portend \cite{portend} is the most closely related work we have found.
Based on single-pass data race reports, it tests alternate program executions to classify candidates in a taxonomy of likely severity.
It uses symbolic execution to test input nondeterminism as well as schedule nondeterminism,
while we explore the latter only.
Portend additionally reports non-failing races which nevertheless cause
%suspiciously
different program output, which is orthogonal to our technique.
However, Portend does not test alternate interleavings {\em in advance} of knowing data races,
which is necessary to expose certain bugs (\sect{\ref{sec:eval-falseneg}}) or to provide full verification (\sect{\ref{sec:totalverif}}).
% XXX: Is this true??
It also assumes the POSIX synchronization API, so cannot verify arbitrary synchronization algorithms such as we do with \mxtest.
Future work could combine the two approaches, using MC to produce new data-race traces for Portend to classify, or using Portend's analysis to inform \quicksand's state space priorities.

@@
